Project 1 Checkpoint

### 2015-01-31 project1/checkpoint/main.tex
Adding bibtex entry for main report
Stubbing out some subsections and adding some assumptions

\section{The Conceptual Model}
Conceptual Model

@@

\cite{pde_solution}
\bibliographystyle{plain}
\bibliography{main}

>>>>

\section{The Conceptual Model}
In order to create a representative software simulation of the aforementioned system, we first begin by designing a
conceptual version of this model from which we can plan our implementation. Let's consider a couple of key aspects
categorically:

\subsection{Simulation Input}

\subsection{Simulation Output}

\subsection{Content}

\subsection{Simplifications and Assumptions}
Probably the most obvious "flaw" in such a design are the simplifications made. Details can certainly be left out
purposely for many reasons such as time constraints, lack of supporting data to model a extra feature, or simply
unneccesary complexity.

In this case, certainly the most prominent would be the ``isolation'' of the model. We are only considering an
idealized random input distribution of cars from both North and South of the 12th St. intersection. However, this is
certainly not the case, since this input distribution is affected by countless other factors like the surrounding
lights, cars passing along 12th at that intersection, and even simply time of day. We assume in this simulation is
perpetually between 4:00PM to 4:15PM in Atlanta (a frightening thought indeed), simply due to the fact that we only
have data for that time range.

@@

\cite{cts12}
\bibliographystyle{plain}
\bibliography{main}
